I/O simulation extension for SimGrid framework

### 2020-04-29 paper_io_sim.tex
Update discussion, add refs

		\subsection{Simulators}
			\begin{itemize}
				\item Discuss some existing methods, simulation frameworks to conduct HPC experiments. Compare pros and cons (accuracy, simulation time, usability) of some simulators (SimGrid, GridSim).
				\item Discuss the pros of SimGrid and the reasons why we chose it to extend.
			\end{itemize}

@@

		\subsection{Experiments}
			Describe data, workflow, number of tasks, task details, environment of each experiment.

@@

			\item Quantized results: 
				\begin{itemize}
					\item Errors of simulation time and memory used compared to real results.
					\item Simulation time compared to baseline SimGrid.
				\end{itemize}

			\item Ability of the model to generalize trends seen in memory (amount of dirty data, page cache) and disk throughput.

@@

	\section{Discussion and Future Work}

\bibliographystyle{plain}
\bibliography{citation}

>>>>

		\subsection{Simulators}
			\begin{itemize}
				\item Discuss some existing methods, simulation frameworks to conduct HPC experiments. Compare pros and cons (accuracy, simulation time, usability) of some simulators (SimGrid, GridSim).
				\item Related development: RAM energy consumption \cite{gill2019} \cite{ouarnoughi2017} 
				\item Discuss the pros of SimGrid and the reasons why we chose it to extend.
			\end{itemize}

@@

		\subsection{Experiments}
			For each experiment: 
			\begin{itemize}
				\item Describe data, workflow, number of tasks, task details, environment of each experiment.
				\item Compare the results from real pipeline, baseline SimGrid  and SimGrid with our extension.
			\end{itemize}

@@

			\item Quantitative results: 
				\begin{itemize}
					\item Errors of simulation time and memory used compared to real results.
					\item Simulation time compared to baseline SimGrid.
				\end{itemize}

			\item Ability of the model to generalize memory trends (dirty data, cache used) and disk throughput.

@@

	\section{Discussion and Future Work}
		\begin{itemize}
			\item Sensitivity of the simulator on the variation of memory and disk bandwidth. 
		\end{itemize}
\bibliographystyle{plain}
\bibliography{citation}
